New cardinality estimation algorithms for HyperLogLog sketches

### 2016-09-01 paper/paper.tex
added new figure to paper

@@

>>>>

The corrected raw estimator beats the precision of methods that use bias correction \cite{Heule2013,Rhodes2015,Sanfilippo2014}. \cref{fig:stdev_comparison} shows the standard deviation of the raw estimator after bias correction. At the transition region to small cardinalities, for which all previous methods switch over to the linear counting estimator at some point, the corrected raw estimator has smaller variance. Obviously, the previous approaches cannot do better than given by the minimum of both curves for linear counting and raw estimator. In practice, the standard deviation is even larger, because the choice between both estimators must be made based on an estimate and not on the true cardinality, for which the intersection point of both curves represents the ideal transition point.

@@

\begin{figure}
\centering
\includesvg[width=1\textwidth]{stdev_comparison}
\caption{Standard deviations of different cardinality estimators as functions of the real cardinality.}
\label{fig:stdev_comparison}
\end{figure}
